Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2014-09-24 ch-tms/tms.tex
inital review revised 1

In this chapter, a TEM-Raman integrated study on \ce{WO3}-\ce{WS2} core-shell nanostructures is presented. We leverage a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates. This technique has enabled us to correlate TEM and micro-Raman measurement on individual nanowires, thereby enhancing the understanding of structure-property relations which would otherwise be blurred in conventional ensemble averaged methods. \ce{WO3}-\ce{WS2} heterostructure is chosen due to the potential applications in photocatalysis and hydrogen evolution.

The remaining section is arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) nanotubes (NTs) and 2D few layer (FL) structures will be introduced first, followed by Raman spectroscopy summary on NTs and FL. The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations, including both ensemble averaged and on individual nanowires. This chapter is concluded with a brief summary and future work.

@@

\subsection{synthesis method in this work}

Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, and sulfur powder was used to fabricate \ce{WO3}-\ce{WS2} core-shell NWs, as summarized in Table.~\ref{tab:ch5pre}. All reactants were employed as received without further processing. Substrates cleaning precudures have been introduced in Sec.~\ref{ch2sub}.

% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{List of reactants}\label{tab:ch5pre}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
\bottomrule
\end{tabular}
\end{table}

@@

\ce{WO3}-\ce{WS2} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs. As depicted in Fig.~\ref{fig:ch5grow}c, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}. After pumping down, the reaction chamber was flushed two times to expel residual air. A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation. Then the furnace was heated to 750 \si{\degreeCelsius} in 30 min, held for 15 min, and allowed to naturally cool down to room temperature. During entire growth process, 30 sccm Ar was used as carrier flow.

@@

\subsubsection{Optimization of W powder oxidization}\label{sec:woxd}

@@

\subsubsection{Seeded growth of tungsten oxide NWs}
With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.

@@

The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism. External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate. The local NW density in oxidation experiment was much higher than that of seeded growth. It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures. At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product. The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained. This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}. The source material in seeded growth is not limited to high purity tungsten powder. Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
\subsubsection{Ensemble measurements on core-shell NWs}

@@

After examining dozens of core-shell NWs, the author found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification. Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW. The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2. Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending. \ce{WS2} fullerene also show similar structures. Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth3}
\caption[TEM imaging on core-shell NWs: 2]{HRTEM imaging on the tip area of one core-shell nanowire.}
\label{fig:ch5ws2tem3}
\end{figure}

@@

A systematic study on the sulfurization must be performed to understand the growth dynamics. The growth mechanism of \ce{WS2} nanotubes from oxides were thoroughly studied,\cite{Feldman1998} and it is generally agreed that the sulfurization of \ce{WO3} is a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs will become non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} In this study, the author recognize this possibility but also consider two factors different from previous studies: one is the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which will accelerate the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other is the short reaction time and light degree of sulfurization, which probably will not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section. The sulfurization dynamic is then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibit greater crystalline disorder, and \ce{WS2} layers on tips are folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body is quasi-one dimensional, subsequently the sulfurization rate could be lower. Besides, sulfurization could also initiated from the NW body, presumably due to the presence of surface defects. As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.

Among most of the core-shell NWs examined under TEM, the author observed no discernible consumed core region. An exception is shown in Fig.~\ref{fig:ch5ws2tem2}. It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model.

@@

\subsection{TEM-Raman integrated study}

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support. A home-built micromanipulator with proble tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100x objective. The steps are visualized in Fig.~\ref{fig:ch5ws2trans}. 
% ws2 transfer
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2trans}
\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. }
\label{fig:ch5ws2trans}
\end{figure}

The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner. Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition was used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but 1 wall is not equal to 1 layer due to the tubular structure). To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m). And the low magnification TEM images and optical images were compared to map the NW location and orientation. The carbon film patterns served as a unique background to resolve possible ambiguity. An example is given in Fig.~\ref{fig:ch5ws2map}. 
% ws2 map
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2map}
\caption[Mapping core-shell NWs]{Core-shell nanowires mapping. }
\label{fig:ch5ws2map}
\end{figure}

Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study. The diameter of these core-shell NWs is around 100 nm and the length around 10 $\mu$m, allowing for up to five distinctive Raman scattering sites. Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation. Two strong peaks were observed between 300 and 450 \si{cm^{-1}}. The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.  Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, \emph{i.e.}, the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}. The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}. Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, \emph{e.g.}, a shoulder mode emerges on the low frequency side of $A_{1g}$ mode. Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}

% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_tem_ram}
\caption[TEM-Raman integrated characterization on core-shell NWs]{(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten. (e) Raman spectra acquired from core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations. Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here). (f) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands. }
\label{fig:ch5ws2ram}
\end{figure}

@@

\section{summary}

\section{literature to read}

@@

\section{literature read}

>>>>

In this chapter, a TEM-Raman integrated study on \ce{WO3}-\ce{WS2} core-shell nanostructures is presented. This study leverages a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates. This technique has enabled us to correlate TEM and micro-Raman measurement on individual nanowires, thereby enhancing the understanding of structure-property relations which would otherwise be blurred in conventional ensemble averaged methods. \ce{WO3}-\ce{WS2} heterostructure is chosen due to the potential applications in photocatalysis and hydrogen evolution.

The remaining section is arranged in following order: a review on the growth of \ce{MS2} (M = Mo, W) nanotubes (NTs) and 2D \gls{fl} structures will be introduced first, followed by Raman spectroscopy summary on \ce{WS2} NTs and FL. The thesis will then focus on synthesis of \ce{WO3}-\ce{WS2} heterostructure and various characterizations on both ensemble and individual nanowires. This chapter is concluded with a brief summary and future work.

@@

\subsection{synthesis Method in This Work}

Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, and sulfur powder was used to fabricate \ce{WO3}-\ce{WS2} core-shell NWs, as summarized in Table.~\ref{tab:ch5pre}. All reactants were employed as received without further processing. Substrates cleaning procedures have been introduced in Sec.~\ref{ch2sub}.

% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{List of reactants for \ce{WO3}-\ce{WS2}}\label{tab:ch5pre}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
\bottomrule
\end{tabular}
\end{table}

@@

\ce{WO3}-\ce{WS2} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs. As depicted in Fig.~\ref{fig:ch5grow}c, the as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$ mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}. After pumping down, the reaction chamber was flushed two times to expel residual air. A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation. Then the furnace was heated to 750 \si{\degreeCelsius} in 30 min, held for 15 min, and allowed to naturally cool down to room temperature. During entire growth process, 30 sccm Ar was used as carrier flow.

@@

\subsubsection{Optimization of W powder Oxidization}\label{sec:woxd}

@@

\subsubsection{Seeded Growth of Tungsten Oxide NWs}
With the oxidation experiments study in Sec.~\ref{sec:woxd}, favorable conditions for local growth of NWs were extracted to perform seeded growth.

@@

The enhanced yield of NWs obtained via seeded growth could be explained by a vapor-solid (VS) mechanism. External supply of growth species will condense onto the powders and substrate simultaneously, promoting the elongation of NWs on power as well as resulting island-layer growth on substrate. The local NW density in oxidation experiment was much higher than that of seeded growth. It is reasonable to presume that during seeded growth, several NWs in a small region on powder will coalescence, as evidenced by the bundled structures. At last, the author would like to point out that when low purity tungsten powder (3N) was used as source, sodium tungsten oxide nanowires were found to be dominant in the final product. The details have been published.\cite{Sheng2014} It seems surprising that when 3N powder was used as seeds, only \ce{WO3} nanowires were obtained. This result was attributed to the lower temperature and significantly reduced amount of 3N powder used in the seeded growth, compared with the conditions used in Ref.\cite{Sheng2014}. The source material in seeded growth is not limited to high purity tungsten powder. Instead, any material that could produce appropriate growth vapor could be employed, indicating the versatility of this approach.
\subsubsection{Ensemble Measurements on Core-Shell NWs}

@@

After examining dozens of core-shell NWs, this thesis found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification. Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW. The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2. Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending. \ce{WS2} fullerene also show similar structures. Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth3}
\caption[TEM imaging on core-shell NWs: 2]{HRTEM imaging on the tip area of one core-shell nanowire.}
\label{fig:ch5ws2tem3}
\end{figure}

@@

A systematic study on the sulfurization must be performed to understand the growth dynamics. The growth mechanism of \ce{WS2} nanotubes from oxides were thoroughly studied,\cite{Feldman1998} and it is generally agreed that the sulfurization of \ce{WO3} is a diffusion limited reaction.\cite{Feldman1996} It was also suggested that the core \ce{WO3} NWs will become non-stoichiometric phases upon sulfurization.\cite{Feldman1996,ZAK2009} This study recognizes this possibility but also consider two factors different from previous studies: one is the usage of sulfur as precursor instead of \ce{H2} and/or \ce{H2S} as in previous reports, which will accelerate the reduction of \ce{WO3} significantly due to the formation of \ce{H2O}; the other is the short reaction time and light degree of sulfurization, which probably will not distort the \ce{WO3} lattice significantly, as evidenced by the XRD and HRTEM analysis in this section. The sulfurization dynamic is then proposed as following in this thesis: the tips of \ce{WO3} NWs exhibit greater crystalline disorder, and \ce{WS2} layers on tips are folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body is quasi-one dimensional, subsequently the sulfurization rate could be lower. Besides, sulfurization could also initiated from the NW body, presumably due to the presence of surface defects. As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.

No obviously consumed core region was observed among most of the core-shell NWs examined under TEM. An exception is shown in Fig.~\ref{fig:ch5ws2tem2}. It is worth mentioning that some interesting growth behavior around the void region, where a new \ce{WS2} layer pushing through the already formed \ce{WS2} ones, deviating from the diffusion growth model.

@@

\subsection{TEM-Raman Integrated Study}\label{tms:raman}

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support. A home-built micromanipulator with proble tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100x objective. The steps are visualized in Fig.~\ref{fig:ch5ws2trans}. 
% ws2 transfer
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2trans}
\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. (a) tungsten tip under X100 objective, (b) NWs dispersed onto PDMS, (c) one NW picked up using tungsten tip and (d) tranferred NW on TEM grid}
\label{fig:ch5ws2trans}
\end{figure}

The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner. Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition was used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but 1 wall is not equal to 1 layer due to the tubular structure). To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m). And the low magnification TEM images and optical images were compared to map the NW location and orientation. The carbon film patterns served as a unique background to resolve possible ambiguity. An example is given in Fig.~\ref{fig:ch5ws2map}. 
% ws2 map
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2map}
\caption[Mapping core-shell NWs]{Core-shell nanowires mapping.  Optical image of one NW on TEM under (a) x100 magnification and (b) digital zoom-in view; (b) Low magnification and (d) high magnification TEM images on the same NW.}
\label{fig:ch5ws2map}
\end{figure}

Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study. The diameter of these core-shell NWs is around 100 nm and the length around 10 $\mu$m, allowing for up to five distinctive Raman scattering sites. Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation. Two strong peaks were observed between 300 and 450 \si{cm^{-1}}. The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.  Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, i.e., the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}. The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}. Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, \emph{e.g.}, a shoulder mode emerges on the low frequency side of $A_{1g}$ mode. Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}

% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{ws2_tem_ram}
\caption[TEM-Raman integrated characterization on core-shell NWs]{(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten. (e) Raman spectra acquired from core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations. Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here). (f) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands. }
\label{fig:ch5ws2ram}
\end{figure}

@@

\section{Summary}

\iffalse

%\section{literature to read}

@@

%\section{literature read}
